Military mechanization as a complex adaptive system

### 2018-07-17 paper2/paper2.tex
recontextualized

	Military mechanization is the degree to which a state's army is comprised of
	ground combat vehicles as opposed to infantry. Mechanization is an important topic 
	in international relations scholarship and a practical concern for
	policymakers. This paper makes novel theoretical contributions by
	re-envisioning mechanization as a complex adaptive system. It implements an
	agent-based model of military mechanization. The results of this model
	challenge the conventional wisdom that mechanization is primarily driven
	by external factors such as security environment.

@@

There is no single universally accepted definition of a complex adaptive system
\citep{miller2009complex}. However, two core features are
that the system is non-decomposable, and that the system features cognitive
agents. The following sections detail how mechanization meets this description.

@@

Human beings learn not only from their own experiences, but also from observing others.
State decisionmakers are no exception. For example, the stunning success of
Coalition precision-guided munitions in the 1991 Gulf War led other states who
were not direct combatants to reform their own militaries
\citep{scobell2011chinese}. There is no guarantee that such emulation always
works out. Consider Ireland: between the 1920s and 1940s, it sought to spend a
large portion of its defense budget on building a small number of
tanks, which at that time were novel technology being implemented by the leading
European militaries. They would have been wholly insufficient to repel a British invasion (their ostensible purpose), 
and Ireland would have been better-served to pursue a low-mechanization guerrilla defense strategy, 
but tanks were seen as a prestigious signifier of a ``real'' professional
military and hence desirable
\citep{farrell1998professionalization,farrell2001transnational}. A more
sophisticated representation of cognition that incorporates such
learning-from-others is needed.

@@

This section of the paper describes the model. It does not use the ODD protocol
of \citet{grimm2006standard} but covers many of the same points.

\subsection{Research question and strategy}

I hypothesize that the arguments of \citet{sechser2010army} are incomplete and
that some omitted variable or set of variables acts as a ``brake'' on 
mechanization.\footnote{By ``omitted'', I mean that Sechser and Saunders conclude that the variable
is not very important for mechanization, not that they do not address the
variable at all.} An agent-based model is used to test this hypothesis. In broad
terms, agents (states) are defined to have the cognitive and learning behavior
implicitly claimed by \citet{sechser2010army}. The model is initialized with
real-world data from 1979 and allowed to run until 2001. The micro- and
macro-outcomes are then validated against real-world 2001 data. If
\citet{sechser2010army} are correct, the model's 2001 outcomes should match
real-world 2001 outcomes. If the model mechanization levels in 2001 are much
higher, then their claimed behavioral rules are incomplete and fail to include
some ``brake'' on mechanization, matching my hypothesis. Proving exactly what
that missing variable or set of variables is is outside the scope of this model
and paper, though it is discussed.
\subsection{Agents}

@@

\subsection{Environment}

@@

\subsection{Cognition}

@@

\subsection{Time}

@@

\subsection{Output Data, Verification, and Validation}

>>>>

	Military mechanization is the degree to which a state's army is comprised of
	ground combat vehicles as opposed to infantry. Mechanization is an important topic 
	in international relations scholarship and a practical concern for
	policymakers. This paper makes novel theoretical contributions by
	re-envisioning mechanization as a complex adaptive system. It implements an
	agent-based model of military mechanization. The results of this model
	both confirm that mechanization is a complex adaptive system and
	challenge the conventional wisdom that mechanization is primarily driven
	by external factors such as security environment.

@@

There is no single universally accepted definition of a complex adaptive system
\citep{miller2009complex}. However, some core features are
that the system is non-decomposable; that the system features autonomous, cognitive
agents; and that the individual behaviors of these agents aggregate upwards into
complex system behavior (e.g., stability, chaos, feedback loops, and the like). 
The following sections detail how mechanization meets the first two parts of
this description (later sections deal with system behavior).

@@

Human beings learn not only from their own experiences, but also from observing others.
State decisionmakers are no exception. For example, the stunning success of
Coalition precision-guided munitions in the 1991 Gulf War led other states who
were not direct combatants to reform their own militaries
\citep{scobell2011chinese}. There is no guarantee that such emulation always
works out. Consider Ireland: between the 1920s and 1940s, it sought to spend a
large portion of its defense budget on building a small number of
tanks, which at that time were novel technology being implemented by the leading
European militaries. They would have been wholly insufficient to repel a British invasion (their ostensible purpose), 
and Ireland would have been better-served to pursue a low-mechanization guerrilla defense strategy, 
but tanks were seen as a prestigious signifier of a ``real'' professional
military and hence desirable
\citep{farrell1998professionalization,farrell2001transnational}.

@@

This section of the paper describes research hypotheses and an agent-based
model used to test them.

\subsection{Research hypotheses}

I hypothesize that the arguments of \citet{sechser2010army} are incomplete and
that some omitted variable or set of variables acts as a ``brake'' on 
mechanization.\footnote{By ``omitted'', I mean that Sechser and Saunders conclude that the variable
is not very important for mechanization, not that they do not address the
variable at all.} An agent-based model is used to test this hypothesis. In broad
terms, agents (states) are defined to have the cognitive and learning behavior
implicitly claimed by \citet{sechser2010army}. The model is initialized with
real-world data from 1979 and allowed to run until 2001. The micro- and
macro-outcomes are then validated against real-world 2001 data. If
\citet{sechser2010army} are correct, the model's 2001 outcomes should match
real-world 2001 outcomes. If the model mechanization levels in 2001 are much
higher, then their claimed behavioral rules are incomplete and fail to include
some ``brake'' on mechanization, matching my hypothesis. Proving exactly what
that missing variable or set of variables is is outside the scope of this model
and paper, though it is discussed.

\subsection{Model}

\subsubsection{Agents}

@@

\subsubsection{Environment}

@@

\subsubsection{Cognition}

@@

\subsubsection{Time}

@@

\subsubsection{Output Data, Verification, and Validation}
